Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-19 ms.tex
still working on describing uncertainty model, also mention DIRBE 140um/240um in data section

@@

\begin{equation}
I_{CO, \nu_i} = \sum\limits_{N} I_{CO, \nu_i, N, N-1}
\end{equation}

@@

\begin{multline}
\sigma^2_{\nu_i}(p) = c^2_{\nu_i}I_{\nu_i}^2(p) + c^2_{\nu_i}\sigma_{CMB, \nu_i}^2 + (\delta O_{\nu_i})^2 \\
+ n_{\nu_i}^2 + \sigma^2_{CIBA, \nu_i} + \sigma^2_{CO, \nu_i}(p)
\end{multline}

@@

This error budget is modeled after \cite{planckdust} Equation 7, but with some 
modifications and additions. The first term accounts for the multiplicative 
uncertainty on the input maps. Table \ref{table:offs} lists the multiplicative 
calibration uncertainty $c_{\nu}$ for each band. These values are taken from 
Table 11 of \cite{planckcalib}. The second term is intended to represent a 
typical uncertainty due to the subtraction of the \verb|SMICA| CMB model. The 
analogous term in \cite{planckdust} Equation 7 is 
($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. a term proportional to CMB model
amplitude. Because this error term's spatial dependence has the potential to 
imprint the CMB anisotropies on the derived parameters, we have chosen to 
replace \verb|SMICA|($p$) with a spatially constant, RMS value for the CMB 
amplitude, $\sigma_{CMB}$. Table \ref{table:offs} lists the adopted values of 
$\sigma_{CMB}$. $\delta O_{\nu_i}$ represents the uncertainty in the band 
$\nu_i$ zero level offset, and the values of $\delta O_{\nu_i}$ can be read 
off from the second column of Table \ref{table:offs}. $n_{\nu_i}$ represents 
the instrumental noise in the pixel of interest, and is taken to be the square 
root of the \verb|ii_cov| parameter that accompanies each \PLANCK~intensity 
map.

>>>>

In some of our FIR dust SED analyses which do not require high angular 
resolution, specifically those of $\S$\ref{sec:global}, $\S$\ref{sec:lores}, 
and $\S$\ref{sec:hier}, we also make use of the SFD reprocessings of DIRBE 
140$\mu$m (2141 GHz) and 240$\mu$m (1250 GHz).

@@

\begin{equation} \label{equ:molcorr}
I_{CO, \nu_i} = \sum\limits_{N} I_{CO, \nu_i, N, N-1}
\end{equation}

@@

\begin{multline}
\sigma^2_{\nu_i}(p) = c^2_{\nu_i}I_{\nu_i}^2(p) + c^2_{\nu_i}\sigma_{CMB, \nu_i}^2 + (\delta O_{\nu_i})^2 \\
+ n_{\nu_i}^2 + \sigma^2_{CO, \nu_i}(p)  + \sigma^2_{CIBA, \nu_i}
\end{multline}

@@

This error budget is modeled after \cite{planckdust} Equation 7, but with some 
modifications and additions. The first term accounts for the multiplicative 
uncertainty on the input maps. Table \ref{table:offs} lists the multiplicative 
calibration uncertainty $c_{\nu}$ for each band. These values are taken from 
Table 11 of \cite{planckcalib}. The second term is intended to represent a 
typical uncertainty due to the subtraction of the \verb|SMICA| CMB model. The 
analogous term in \cite{planckdust} Equation 7 is 
($c_{\nu}$$\times$\verb|SMICA|($p$))$^2$, i.e. an uncertainty proportional to 
the CMB model amplitude in each pixel. Because this term's spatial dependence 
has the potential to imprint the CMB anisotropies on the derived parameters, we
have chosen to replace \verb|SMICA|($p$) with a spatially constant, RMS value 
for the CMB amplitude, $\sigma_{CMB}$. Table \ref{table:offs} lists the adopted
values of $\sigma_{CMB}$. $\delta O_{\nu_i}$ represents the uncertainty in the 
band $\nu_i$ zero level offset, and the values of $\delta O_{\nu_i}$ can be 
read off from the second column of Table \ref{table:offs}. $n_{\nu_i}$ 
represents the instrumental noise in the pixel of interest, and is taken to be 
the square root of the \verb|ii_cov| parameter that accompanies each 
\PLANCK~intensity map. The next term accounts for the uncertainty on the 
CO emission correction, with $\sigma_{CO, \nu_i}$=0.15$\times$$I_{CO, \nu_i}$
(see $\S$\ref{sec:mole}, specifically Equation \ref{equ:molcorr}).
